---
title: "Group_05_Aggregate_Data_Files"
author: "Lewis O. Harvey, Jr."
date: "21 February 2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library("tidyverse")

rm(list = ls())

```

R code for combining the data from the individual subject's csv data files from PsychoPy into one data frame, and writing that data frame out to a single csv file. The participant column, which contains the subject's initials, is replaced by a subject number to preserve anonymity. This subject number is randomly assigned among the `n` data files.

you can customize this script in three major ways:

1. You must specify the folder that contains the data files to be combined
2. You can change the name of the output file (file.output) below
3. specify which of the many columns produced by PsychoPy in the csv file to keep by modifying the vector of column names stored in object 'keep'.


```{r}
# name of output file (change the name if you want to)
file.output <- "group_05_aggregated_data.csv"

# turn off randomizing order of subjects
# helps locate problem files.
# Set to TRUE when all the problems are solved
RANDOMIZE <- TRUE

## find folder with the data files
path_name <- "data folder name goes here"

# make a list of just the csv files
filelist <- list.files(path = path_name, pattern = "\\.csv")

# calculate the number of subjects
n.subjects <- length(filelist)

# create vector of 1:n subject numbers in random order
if(RANDOMIZE) {
    subject.no <- sample(1:n.subjects)
} else {
    subject.no <- 1:n.subjects
}

# create a vector of subject identifiers 
# to be used in place of initials
subjID <- str_c("s", str_pad(subject.no, width, 2, pad = "0"))

```

```{r}

msg <- paste("Number of files to be aggregated =", n.subjects)
print(msg)

# loop through all the data files and create
# one data frame from all of them

# you can eliminate some of the columns if you know which ones you want to keep
# change the names as appropriate in 'keep' below to save those columns and
# then uncomment the "keep" line below. Of course you will have to change these
# names to match the data from your experiment

keep <- c("participant", "Word", "Valence", "Arousal", "Emotion",
          "Word_Frequency", "Correct_Answer", "Correct_Response",
          "key_resp_4.keys", "key_resp_4.corr", "key_resp_4.rt",
          "date", "psychopyVersion", "frameRate")

```

`r msg`

```{r}

df.all <- data.frame()
file.count <- 0
for (fn in filelist) {
    file.count <- file.count + 1
    print(paste("processing file no.", file.count, "  ", fn,
                "   subject number", subject.no[file.count]))
    # read file
    tmp <- read.csv(file.path(path_name, fn)) %>%
        # remove the 2 rows with no words
        filter(Word != "") %>%
        # put anonymized subjID into the participant column
        mutate(participant = subjID[file.count]) %>%
        # remove factor levels that are empty
        droplevels() %>%
        # get rid of X column if present
        select(-matches("X")) 
    
    # keep desire columns
    ## if you get an error message that 'all_of()' is not found
    ## delete the line below and remove the comment marker from the
    ## line below it
    if (exists('keep')) tmp <- select(tmp, all_of(keep))
    # if (exists('keep')) tmp <- select(tmp, keep)
    
    # add this subject to data frame df.all
    df.all <- rbind(df.all, tmp)
}

df.all <- df.all %>% 
    # make participant a factor
    mutate(participant = factor(participant)) %>% 
    # reorder the subjects by ID value, placing them in random order
    # to make them even more anonymous
    arrange(participant)

write.csv(df.all, file.output, row.names = FALSE)

print(paste("aggregated data written to file '", file.output, "'", sep = ""))

```


